---
title: "Vignette Title"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "# "
)
library(mapdeck)
access_token <- read.dcf("~/Documents/.googleAPI", fields= "MAPBOX")
```


### What is Mapdeck?

Mapdeck is a combination of [Mabox](https://www.mapbox.com/help/define-mapbox-gl/) and [Deck.gl](http://deck.gl/#/)


### Why did you build it?

Because Deck.gl is one of the most user-friendly WebGL javascript libraries and can produce some beautiful maps. And it integrates nicely with Mapbox maps. 



### The basics

Simply calling `mapdeck()` gives you a map

```{r, fig.width=6}
mapdeck(token = access_token)
```

You can style the map using any [mapbox style](https://www.mapbox.com/api-documentation/#styles) template styles, or you can [create one of your own](https://www.mapbox.com/help/studio-manual-styles/)

```{r, fig.width=6}
mapdeck(token = access_token, style = 'mapbox://styles/mapbox/dark-v9')
```



### Shiny

Of course you can, what would be the point otherwise? 

```{r, eval = FALSE}
library(shiny)
token <- "MAPBOX_KEY"
ui <- fluidRow(mapdeckOutput(outputId = "map"))
server <- function(input, output) output$map <- renderMapdeck({ mapdeck(token = token) })
shinyApp(ui, server)
```
