---
title: "Vignette Title"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "# "
)
library(mapdeck)
access_token <- 'pk.eyJ1Ijoic3ltYm9saXgiLCJhIjoiY2pqbm45Zmo1MGl1aTNxbmxwamFqb3Z6MSJ9.yIkj0tGNNh4u61DliOXV6g'
```


### What is Mapdeck?

Mapdeck is a combination of [Mabox](https://www.mapbox.com/help/define-mapbox-gl/) and [Deck.gl](http://deck.gl/#/)


### Why did you build it?

Because Deck.gl is one of the most user-friendly WebGL javascript libraries and can produce some beautiful maps. And it integrates nicely with Mapbox maps. 



### The basics

Simply calling `mapdeck()` gives you a map

```{r, fig.width=6}
mapdeck(token = access_token)
```

You can style the map using any [mapbox style](https://www.mapbox.com/api-documentation/#styles) template styles, or you can [create one of your own](https://www.mapbox.com/help/studio-manual-styles/)

```{r, fig.width=6}
mapdeck(token = access_token, style = 'mapbox://styles/mapbox/dark-v9')
```

### Arcs

```{r, fig.width=6}

key <- "pk.eyJ1Ijoic3ltYm9saXgiLCJhIjoiY2pqbm45Zmo1MGl1aTNxbmxwamFqb3Z6MSJ9.yIkj0tGNNh4u61DliOXV6g"

url <- 'https://raw.githubusercontent.com/plotly/datasets/master/2011_february_aa_flight_paths.csv'
flights <- read.csv(url)
flights$id <- seq_len(nrow(flights))
flights$stroke <- sample(1:3, size = nrow(flights), replace = T)

mapdeck( token = key, style = 'mapbox://styles/mapbox/dark-v9', pitch = 45 ) %>%
	add_arc(
		data = flights
		, layer_id = "arc_layer"
		, origin = c("start_lon", "start_lat")
		, destination = c("end_lon", "end_lat")
		, stroke_from = "airport1"
		, stroke_to = "airport2"
		, stroke_width = "stroke"
	)



```


### Scatter

```{r, fig.width = 6}
key <- "pk.eyJ1Ijoic3ltYm9saXgiLCJhIjoiY2pqbm45Zmo1MGl1aTNxbmxwamFqb3Z6MSJ9.yIkj0tGNNh4u61DliOXV6g"

mapdeck( token = key, style = 'mapbox://styles/mapbox/dark-v9', pitch = 45 ) %>%
add_scatterplot(
  data = capitals
  , lat = "lat"
  , lon = "lon"
  , radius = 100000
  , fill_colour = "country"
  , layer_id = "scatter_layer"
)

```


### Path

Currently only encoded polylines are supported. 

```{r, fig.width = 6}

key <- "pk.eyJ1Ijoic3ltYm9saXgiLCJhIjoiY2pqbm45Zmo1MGl1aTNxbmxwamFqb3Z6MSJ9.yIkj0tGNNh4u61DliOXV6g"

mapdeck(
  token = key
  , style = 'mapbox://styles/mapbox/dark-v9'
  , location = c(145.688269, -38.101062)
  , zoom = 8) %>%
  add_path(
  data = roads
  , polyline = "geometry"
  , stroke_colour = "RIGHT_LOC"
  , layer_id = "path_layer"
)

```

### Polygons

```{r, fig.width = 6}
mapdeck(
  token = key
  , style = 'mapbox://styles/mapbox/dark-v9'
  , location = c(145, -38)
  , zoom = 8
  ) %>%
  add_polygon(
  	data = melbourne
    , polyline = "geometry"
    , layer = "polygon_layer"
  	, fill_colour = "fillColor"
 	)
```


### Multiple layers


```{r, fig.width = 6}

df1 <- capitals[ capitals$country == "Australia", ]
df2 <- capitals[ capitals$country != "Australia", ]
df1$key <- 1
df2$key <- 1

df <- merge(df1, df2, by = 'key')

mapdeck(
  token = key
  , style = 'mapbox://styles/mapbox/dark-v9'
  , pitch = 35
  ) %>%
	add_arc(
		data = df
		, origin = c("lon.x", "lat.x")
		, destination = c("lon.y", "lat.y")
		, layer_id = "arc_layer"
		, stroke_from = "country.x"
		, stroke_to = "country.y"
		, stroke_width = 2
	) %>%
	add_scatterplot(
		data = df2
		, lon = "lon"
		, lat = "lat"
		, radius = 100000
		, fill_colour = "country"
	)


```


### Shiny

watch this space!

It works... but need to figure out data updates and update triggers... 
