---
title: "Vignette Title"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "# "
)
library(mapdeck)
access_token <- 'pk.eyJ1Ijoic3ltYm9saXgiLCJhIjoiY2pqbm45Zmo1MGl1aTNxbmxwamFqb3Z6MSJ9.yIkj0tGNNh4u61DliOXV6g'
```


### What is Mapdeck?

Mapdeck is a combination of [Mabox](https://www.mapbox.com/help/define-mapbox-gl/) and [Deck.gl](http://deck.gl/#/)


### Why did you build it?

Because Deck.gl is one of the most user-friendly WebGL javascript libraries and can produce some beautiful maps. And it integrates nicely with Mapbox maps. 



### The basics

Simply calling `mapdeck()` gives you a map

```{r, fig.width=6}
mapdeck(token = access_token)
```

You can style the map using any [mapbox style](https://www.mapbox.com/api-documentation/#styles) template styles, or you can [create one of your own](https://www.mapbox.com/help/studio-manual-styles/)

```{r, fig.width=6}
mapdeck(token = access_token, style = 'mapbox://styles/mapbox/dark-v9')
```

### Arcs

```{r, fig.width=6}
url <- 'https://raw.githubusercontent.com/plotly/datasets/master/2011_february_aa_flight_paths.csv'
flights <- read.csv(url)
flights$id <- seq_len(nrow(flights))
flights$stroke <- sample(1:3, size = nrow(flights), replace = T)

mapdeck( token = access_token, style = 'mapbox://styles/mapbox/dark-v9', pitch = 45 ) %>%
	add_arc(
		data = flights
		, lat_from = "start_lat"
		, lon_from = "start_lon"
		, lat_to = "end_lat"
		, lon_to = "end_lon"
		, stroke_from = "airport1"
		, stroke_to = "airport2"
		, stroke_width = "stroke"
	)


```

### Shiny

Of course you can, what would be the point otherwise? 

```{r, eval = FALSE}
library(shiny)
token <- "MAPBOX_KEY"
ui <- fluidRow(mapdeckOutput(outputId = "map"))
server <- function(input, output) output$map <- renderMapdeck({ mapdeck(token = token) })
shinyApp(ui, server)
```
